---
title: "Shiny Precomputed Values"
author: Hao Mou (haomou2)
date: "Fall 2022"
output:
  html_document:
    toc: yes
---

In the Shiny App, there are a number of values that can be pre-computed,
I will detail how these values are computed in this document.

First, let's load the libraries and the data.

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(recommenderlab)
library(DT)
library(data.table)
library(reshape2)

set.seed(8998)
```

```{r}
myurl = "https://liangfgithub.github.io/MovieData/"

# Ratings data
ratings = read.csv(paste0(myurl, 'ratings.dat?raw=true'), 
                   sep = ':',
                   colClasses = c('integer', 'NULL'), 
                   header = FALSE)
colnames(ratings) = c('UserID', 'MovieID', 'Rating', 'Timestamp')

# Movies data
movies = readLines(paste0(myurl, 'movies.dat?raw=true'))
movies = strsplit(movies, split = "::", fixed = TRUE, useBytes = TRUE)
movies = matrix(unlist(movies), ncol = 3, byrow = TRUE)
movies = data.frame(movies, stringsAsFactors = FALSE)
colnames(movies) = c('MovieID', 'Title', 'Genres')

movies$MovieID = as.integer(movies$MovieID)
movies$Title = iconv(movies$Title, "latin1", "UTF-8")
movies$Year = as.numeric(unlist(
  lapply(movies$Title, function(x) substr(x, nchar(x)-4, nchar(x)-1))))

# User data
users = read.csv(paste0(myurl, 'users.dat?raw=true'),
                 sep = ':', header = FALSE)
users = users[, -c(2,4,6,8)] # skip columns
colnames(users) = c('UserID', 'Gender', 'Age', 'Occupation', 'Zip-code')
```

# System I results

Since system I only depends on a single input: the genre, we can pre-compute
the recommended movies for each genre so that they don't need to be calculated
at run time.
I will use popularity as measured by the number of ratings for system I.

```{r}
# Add genre matrix to movies
genres = as.data.frame(movies$Genres, stringsAsFactors=FALSE)
tmp = as.data.frame(tstrsplit(genres[,1], '[|]',
                              type.convert=TRUE),
                    stringsAsFactors=FALSE)
genre_list = c("Action", "Adventure", "Animation", 
               "Children's", "Comedy", "Crime",
               "Documentary", "Drama", "Fantasy",
               "Film-Noir", "Horror", "Musical", 
               "Mystery", "Romance", "Sci-Fi", 
               "Thriller", "War", "Western")
m = length(genre_list)
genre_matrix = matrix(0, nrow(movies), length(genre_list))
for(i in 1:nrow(tmp)){
  genre_matrix[i,genre_list %in% tmp[i,]]=1
}
colnames(genre_matrix) = genre_list
remove("tmp", "genres")
movies = cbind(movies, genre_matrix)

# Add average ratings and rating counts to movies
movies = ratings %>%
  group_by(MovieID) %>% 
  summarize(ratings_per_movie = n(), ave_ratings = mean(Rating)) %>%
  inner_join(movies, by = "MovieID")
```

```{r}
# The scheme
top_n_by_popularity = function(genre, n) {
  movies %>% 
    filter(movies[genre] == 1) %>%
    slice_max(ratings_per_movie, n = n, with_ties = FALSE) %>%
    select(c("MovieID"))
}

# Precompute
system1.res = list()
for(genre in genre_list){
  system1.res[genre] = top_n_by_popularity(genre, 10)
}

saveRDS(system1.res, file = "rds/system1.res.RDS")
```


# Most popular movies

The most popular movies will be used in System II to ask users for initial
ratings.

```{r}
popular.120 = movies %>%
  slice_max(ratings_per_movie, n = 120, with_ties = FALSE) %>%
  select(c("MovieID"))

saveRDS(popular.120, file = "rds/popular.120.RDS")
```

# System II IBCF model

I will be using IBCF for System II and the IBCF model can be pre-trained.

```{r}
i = paste0('u', ratings$UserID)
j = paste0('m', ratings$MovieID)
x = ratings$Rating
tmp = data.frame(i, j, x, stringsAsFactors = T)
Rmat = sparseMatrix(as.integer(tmp$i), as.integer(tmp$j), x = tmp$x)
rownames(Rmat) = levels(tmp$i)
colnames(Rmat) = levels(tmp$j)
Rmat = new('realRatingMatrix', data = Rmat)

recommender.IBCF = Recommender(Rmat, method = "IBCF",
                               parameter = list(normalize = 'center', 
                                                method = 'Cosine', 
                                                k = 30))

saveRDS(recommender.IBCF, file = "rds/recommender.IBCF.RDS")
```

